---
title: "Final Result"
author: "Raphael Jeong-Hin Chin"
date: "04/14/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

# Libraries

This code chunk should be run if rmd file is opened on a virtual site. 

```{r Installations}
# install.packages(c("tidyverse","CDM","cdmTools","matlab","reticulate","plotly","foreach","doParallel"))
```

Libraries used in this rmd file:

```{r Libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(cdmTools)   # estQ, orderQ
library(CDM)        # gdina
library(matlab)     # matrix
library(MASS)       # mvrnorm
library(reticulate) # python
library(plotly)     # ggplotly
```

# Dataset 

Reading in data. 

```{r data, warning=FALSE, message=FALSE}
filenames <- list.files(pattern="*.csv")

for (i in filenames){
  assign(i, read.csv(file = i,header = TRUE))
}

```

<!-- # Aggregating  -->

<!-- Some of the files contain raw data which haven't been aggregated to find the mean -->

<!-- ```{r} -->
<!-- RBM_Mean_Rho0_03172022.csv <- RBM_Mean_Rho0_03172022.csv %>% group_by(Lambda,Eta) %>% summarise(Similarity = mean(Similarity)) -->
<!-- RBM_Mean_Rho015_03172022.csv <- RBM_Mean_Rho015_03172022.csv %>% group_by(Lambda,Eta) %>% summarise(Similarity = mean(Similarity)) -->
<!-- RBM_Mean_Rho025_03172022.csv <- RBM_Mean_Rho025_03172022.csv %>% group_by(Lambda,Eta) %>% summarise(Similarity = mean(Similarity)) -->

<!-- RBM_Mean_N1000_Rho0_03172022.csv <- RBM_Mean_N1000_Rho0_03172022.csv %>% group_by(Lambda,Eta) %>% summarise(Similarity = mean(Similarity)) -->
<!-- RBM_Mean_N1000_Rho015_03172022.csv <- RBM_Mean_N1000_Rho015_03172022.csv %>% group_by(Lambda,Eta) %>% summarise(Similarity = mean(Similarity)) -->
<!-- RBM_Mean_N1000_Rho025_03172022.csv <- RBM_Mean_N1000_Rho025_03172022.csv %>% group_by(Lambda,Eta) %>% summarise(Similarity = mean(Similarity)) -->
<!-- ``` -->

# CDM  {.tabset}

## K = 3  {.tabset}

All simulations were run 50 times

### Lasso  {.tabset}

#### N = 500 

Threshold = 0.1

```{r}
ggplotly(ggplot() +
  geom_line(data=CDM_Lasso_Mean_K3_N500_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_point(data=CDM_Lasso_Mean_K3_N500_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_line(data=CDM_Lasso_Mean_K3_N500_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_point(data=CDM_Lasso_Mean_K3_N500_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_line(data=CDM_Lasso_Mean_K3_N500_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_point(data=CDM_Lasso_Mean_K3_N500_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_line(data=CDM_Lasso_Mean_K3_N500_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  geom_point(data=CDM_Lasso_Mean_K3_N500_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  scale_color_manual(name="Rho", values = c("red","blue","green","purple")) )
```

#### N = 1000 

Threshold = 0.1

```{r}
ggplotly(ggplot() +
  geom_line(data=CDM_Lasso_Mean_K3_N1000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_point(data=CDM_Lasso_Mean_K3_N1000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_line(data=CDM_Lasso_Mean_K3_N1000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_point(data=CDM_Lasso_Mean_K3_N1000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_line(data=CDM_Lasso_Mean_K3_N1000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_point(data=CDM_Lasso_Mean_K3_N1000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_line(data=CDM_Lasso_Mean_K3_N1000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  geom_point(data=CDM_Lasso_Mean_K3_N1000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  scale_color_manual(name="Rho", values = c("red","blue","green","purple")) )
```


#### N = 2000

Threshold = 0.1

```{r}
ggplotly(ggplot() +
  geom_line(data=CDM_Lasso_Mean_K3_N2000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_point(data=CDM_Lasso_Mean_K3_N2000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_line(data=CDM_Lasso_Mean_K3_N2000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_point(data=CDM_Lasso_Mean_K3_N2000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_line(data=CDM_Lasso_Mean_K3_N2000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_point(data=CDM_Lasso_Mean_K3_N2000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_line(data=CDM_Lasso_Mean_K3_N2000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  geom_point(data=CDM_Lasso_Mean_K3_N2000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  scale_color_manual(name="Rho", values = c("red","blue","green","purple")) )
```



### TLP {.tabset}

#### N = 500

Threshold = 0.1

```{r}
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N500_Rho0_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N500_Rho015_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N500_Rho025_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N500_Rho050_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))
```


#### N = 1000

Threshold = 0.1

```{r}
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N1000_Rho0_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N1000_Rho015_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N1000_Rho025_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N1000_Rho050_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))

```

#### N = 2000

Threshold = 0.1

```{r}
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N2000_Rho0_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N2000_Rho015_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N2000_Rho025_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K3_N2000_Rho050_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))

```

## K = 4 {.tabset}

### Lasso  {.tabset}

#### N = 1000 

Threshold = 0.1

```{r}
ggplotly(ggplot() +
  geom_line(data=CDM_Lasso_Mean_K4_N1000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_point(data=CDM_Lasso_Mean_K4_N1000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_line(data=CDM_Lasso_Mean_K4_N1000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_point(data=CDM_Lasso_Mean_K4_N1000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_line(data=CDM_Lasso_Mean_K4_N1000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_point(data=CDM_Lasso_Mean_K4_N1000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_line(data=CDM_Lasso_Mean_K4_N1000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  geom_point(data=CDM_Lasso_Mean_K4_N1000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  scale_color_manual(name="Rho", values = c("red","blue","green","purple")) )

```

#### N = 2000

Threshold = 0.1

```{r}
ggplotly(ggplot() +
  geom_line(data=CDM_Lasso_Mean_K4_N2000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_point(data=CDM_Lasso_Mean_K4_N2000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_line(data=CDM_Lasso_Mean_K4_N2000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_point(data=CDM_Lasso_Mean_K4_N2000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_line(data=CDM_Lasso_Mean_K4_N2000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_point(data=CDM_Lasso_Mean_K4_N2000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_line(data=CDM_Lasso_Mean_K4_N2000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  geom_point(data=CDM_Lasso_Mean_K4_N2000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  scale_color_manual(name="Rho", values = c("red","blue","green","purple")) )

```

### TLP {.tabset}

#### N = 1000

Threshold = 0.1

```{r}
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N1000_Rho0_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N1000_Rho015_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N1000_Rho025_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N1000_Rho050_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))

```

#### N = 2000

Threshold = 0.1

!!! Rho = 0, 0.25 can't be compiled

```{r}

ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N2000_Rho0_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N2000_Rho015_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N2000_Rho025_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K4_N2000_Rho050_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))

```

## K = 5 {.tabset}

### Lasso  {.tabset}

#### N = 1000 

Threshold = 0.1

```{r}
ggplotly(ggplot() +
  geom_line(data=CDM_Lasso_Mean_K5_N1000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_point(data=CDM_Lasso_Mean_K5_N1000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_line(data=CDM_Lasso_Mean_K5_N1000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_point(data=CDM_Lasso_Mean_K5_N1000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_line(data=CDM_Lasso_Mean_K5_N1000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_point(data=CDM_Lasso_Mean_K5_N1000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_line(data=CDM_Lasso_Mean_K5_N1000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  geom_point(data=CDM_Lasso_Mean_K5_N1000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  scale_color_manual(name="Rho", values = c("red","blue","green","purple")) )

```

#### N = 2000

Threshold = 0.1

!!! Rho = 0.25 can't be compiled

```{r}
ggplotly(ggplot() +
  geom_line(data=CDM_Lasso_Mean_K5_N2000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_point(data=CDM_Lasso_Mean_K5_N2000_Rho0_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0"))+
  geom_line(data=CDM_Lasso_Mean_K5_N2000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_point(data=CDM_Lasso_Mean_K5_N2000_Rho015_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.15"))+
  geom_line(data=CDM_Lasso_Mean_K5_N2000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_point(data=CDM_Lasso_Mean_K5_N2000_Rho025_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.25"))+
  geom_line(data=CDM_Lasso_Mean_K5_N2000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  geom_point(data=CDM_Lasso_Mean_K5_N2000_Rho050_t01_04142022.csv, aes(x=Lambda, y=Similarity, color ="0.5"))+
  scale_color_manual(name="Rho", values = c("red","blue","green","purple")) )
```

### TLP {.tabset}

#### N = 1000

Threshold = 0.1

```{r}
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N1000_Rho0_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N1000_Rho015_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N1000_Rho025_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N1000_Rho050_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))

```

#### N = 2000

Threshold = 0.1

```{r}
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N2000_Rho0_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N2000_Rho015_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N2000_Rho025_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = CDM_TLP_Mean_K5_N2000_Rho050_t01_04142022.csv,
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Tau)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.5"))
```

# RBM

## K = 3 {.tabset}

### N = 500

```{r}
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N500_Rho0_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N500_Rho015_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N500_Rho025_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N500_Rho050_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.50"))

```

### N = 1000

```{r}
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N1000_Rho0_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N1000_Rho015_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N1000_Rho025_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N1000_Rho050_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.50"))

```

### N = 2000

```{r}
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N2000_Rho0_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N2000_Rho015_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N2000_Rho025_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_N2000_Rho050_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.50"))

```

## K = 4 {.tabset}

### N = 1000

```{r}
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N1000_Rho0_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N1000_Rho015_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N1000_Rho025_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N1000_Rho050_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.50"))
```

### N = 2000

```{r}
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N2000_Rho0_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N2000_Rho015_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N2000_Rho025_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K4N2000_Rho050_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.50"))
```

## K = 5 {.tabset}

### N = 1000

```{r}
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N1000_Rho0_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N1000_Rho015_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N1000_Rho025_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N1000_Rho050_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.50"))
```

### N = 2000

```{r}
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N2000_Rho0_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N2000_Rho015_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.15"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N2000_Rho025_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.25"))
ggplotly(ggplot()+geom_bar(data = RBM_Mean_K5N2000_Rho050_04142022.csv, 
                           mapping = aes(x = Lambda,y = Similarity, fill = as.factor(Eta)),
                           stat = "identity", position=position_dodge())+ ggtitle("Rho = 0.50"))
```
# Comparing

## K = 3 {.tabset}

### N = 500 ; Rho = 0

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N500_Rho0_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N500_Rho0_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N500_Rho0_04142022.csv$Similarity)))
```

### N = 500 ; Rho = 0.15

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N500_Rho015_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N500_Rho015_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N500_Rho015_04142022.csv$Similarity)))
```

### N = 500 ; Rho = 0.25

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N500_Rho025_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N500_Rho025_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N500_Rho025_04142022.csv$Similarity)))
```
### N = 500 ; Rho = 0.5

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N500_Rho050_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N500_Rho050_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N500_Rho050_04142022.csv$Similarity)))
```


### N = 1000 ; Rho = 0

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N1000_Rho0_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N1000_Rho0_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N1000_Rho0_04142022.csv$Similarity)))
```

### N = 1000 ; Rho = 0.15

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N1000_Rho015_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N1000_Rho015_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N1000_Rho015_04142022.csv$Similarity)))
```

### N = 1000 ; Rho = 0.25

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N1000_Rho025_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N1000_Rho025_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N1000_Rho025_04142022.csv$Similarity)))
```
### N = 1000 ; Rho = 0.5

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N1000_Rho050_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N1000_Rho050_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N1000_Rho050_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N2000_Rho0_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N2000_Rho0_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N2000_Rho0_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0.15

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N2000_Rho015_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N2000_Rho015_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N2000_Rho015_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0.25

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N2000_Rho025_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N2000_Rho025_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N2000_Rho025_04142022.csv$Similarity)))
```
### N = 2000 ; Rho = 0.5

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K3_N2000_Rho050_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K3_N2000_Rho050_t01_04142022.csv$Similarity),
                              max(RBM_Mean_N2000_Rho050_04142022.csv$Similarity)))
```
## K = 4 {.tabset}

### N = 1000 ; Rho = 0

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N1000_Rho0_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N1000_Rho0_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N1000_Rho0_04142022.csv$Similarity)))
```

### N = 1000 ; Rho = 0.15

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N1000_Rho015_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N1000_Rho015_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N1000_Rho015_04142022.csv$Similarity)))
```

### N = 1000 ; Rho = 0.25

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N1000_Rho025_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N1000_Rho025_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N1000_Rho025_04142022.csv$Similarity)))
```
### N = 1000 ; Rho = 0.5

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N1000_Rho050_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N1000_Rho050_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N1000_Rho050_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N2000_Rho0_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N2000_Rho0_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N2000_Rho0_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0.15

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N2000_Rho015_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N2000_Rho015_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N2000_Rho015_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0.25

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N2000_Rho025_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N2000_Rho025_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N2000_Rho025_04142022.csv$Similarity)))
```
### N = 2000 ; Rho = 0.5

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K4_N2000_Rho050_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K4_N2000_Rho050_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K4N2000_Rho050_04142022.csv$Similarity)))
```

## K = 5 {.tabset}

### N = 1000 ; Rho = 0

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N1000_Rho0_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N1000_Rho0_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N1000_Rho0_04142022.csv$Similarity)))
```

### N = 1000 ; Rho = 0.15

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N1000_Rho015_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N1000_Rho015_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N1000_Rho015_04142022.csv$Similarity)))
```

### N = 1000 ; Rho = 0.25

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N1000_Rho025_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N1000_Rho025_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N1000_Rho025_04142022.csv$Similarity)))
```
### N = 1000 ; Rho = 0.5

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N1000_Rho050_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N1000_Rho050_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N1000_Rho050_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N2000_Rho0_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N2000_Rho0_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N2000_Rho0_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0.15

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N2000_Rho015_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N2000_Rho015_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N2000_Rho015_04142022.csv$Similarity)))
```

### N = 2000 ; Rho = 0.25

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N2000_Rho025_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N2000_Rho025_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N2000_Rho025_04142022.csv$Similarity)))
```
### N = 2000 ; Rho = 0.5

```{r}
data.frame(model      = c("Lasso","TLP","RBM"),
               Similarity = c(max(CDM_Lasso_Mean_K5_N2000_Rho050_t01_04142022.csv$Similarity),
                              max(CDM_TLP_Mean_K5_N2000_Rho050_t01_04142022.csv$Similarity),
                              max(RBM_Mean_K5N2000_Rho050_04142022.csv$Similarity)))
```
